Influences of GDP in the U.S

### 2022-11-14 Manuscript/manuscript.tex
commit

\begin{figure}[H]
  \centering
  \includegraphics[scale = .5]{res1}
  \caption{This figure shows the Residuals vs. Fitted plot for Model 1}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale = .5]{norm1}
  \caption{This figure shows the Q-Q Plot for Model 1}
\end{figure}

@@

@@

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[scale = .35]{res1}
  \caption{This figure shows the Residuals vs. Fitted plot for Model 1}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale = .35]{norm1}
  \caption{This figure shows the Q-Q Plot for Model 1}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale = .35]{res2}
  \caption{This figure shows the Residuals vs. Fitted plot for Model 2}
\end{figure}

From this plot, the assumption of homoscedacity is questionable
The residuals do not appear to be randomly scattered throughout the entire plot, and there could be a noticle pattern in some parts of the plot. 
This warrents further invesigation.

\begin{figure}[H]
  \centering
  \includegraphics[scale = .35]{norm2}
  \caption{This figure shows the Q-Q Plot for Model 2}
\end{figure}

@@

The summary statistics for Model 1 application with Validation data are as follows:

\begin{figure}[H]
  \centering
  \includegraphics[scale = .35]{mod1v}
  \caption{This figure shows the summary statistics for Model 1 application to the validation dataset.}
\end{figure}

The summary statistics for Model 2 application with Validation data are as follows:

\begin{figure}[H]
  \centering
  \includegraphics[scale = .35]{mod2v}
  \caption{This figure shows the summary statistics for Model 2 application to the validation dataset.}
\end{figure}
